Subject-specific curves for time series forecasting of smart meter demand

### 2019-11-13 sscts-paper-1.Rmd
Tidy SSCTS. Fix paragraph overflow. Convert table from markdown to latex.

@@

Table: (\#tab:weather-vars) Predictor variables evaluated during feature selection stage when determining $\mathcal{P}_t$.

Variable $x_{b,i,t}$ | Lag (15-minute periods) | Description
----------------|---------|-------------------------------------------------
$w_{b,0,t}$     | 0       | Scaled current temperature.
$w_{b,12,t}$    | 12      | Scaled temperature lagged by 3 hours.
$w_{b,24,t}$    | 24      | Scaled temperature lagged by 6 hours.
$w_{b,48,t}$    | 48      | Scaled temperature lagged by 12 hours.
$w_{b,96,t}$    | 96      | Scaled temperature lagged by 24 hours.
$w_{b,192,t}$   | 192     | Scaled temperature lagged by 2 days.
$w_{b,288,t}$   | 288     | Scaled temperature lagged by 3 days.
$w^+_{b,t}$     |         | Maximum scaled temperature over last 24 hours.
$w^-_{b,t}$     |         | Minimum scaled temperature over last 24 hours.
$\bar{w}_{b,t}$ |         | Average scaled temperature over last 3 days.
$y_{b,96,t}$    | 96      | Scaled actual demand lagged by 1 day.
$y_{b,192,t}$   | 192     | Scaled actual demand lagged by 2 days.
$y_{b,672,t}$   | 672     | Scaled actual demand lagged by 1 week.

@@

When comparing these metrics in Section \@ref(forecasting-accuracy), we do find that the SSCATTR model produces the best point forecasts. To establish that this result is statistically significant we also carry out Diebold-Mariano tests against the ILR model in Section \@ref(diebold-mariano-test).

@@

(ref:accuracy-results) Forecasting accuracy measures for each model across the entire day, business hours (7:00 am to 7:00 pm) and non-business hours (7:00 pm to 7:00 am). The lowest

>>>>

\begin{table}[t]
\caption{\label{tab:weather-vars} Predictor variables evaluated during feature selection stage when determining $\mathcal{P}_t$.}

\centering
\begin{tabular}{lllll}
\toprule
Variable $x_{b,i,t}$ & Lag (15-minute periods) & Description \\
\midrule
$w_{b,0,t}$ & 0 & Scaled current temperature. \\
$w_{b,12,t}$ & 12 & Scaled temperature lagged by 3 hours. \\
$w_{b,24,t}$ & 24 & Scaled temperature lagged by 6 hours. \\
$w_{b,48,t}$ & 48 & Scaled temperature lagged by 12 hours. \\
$w_{b,96,t}$ & 96 & Scaled temperature lagged by 24 hours. \\
$w_{b,192,t}$ & 192 & Scaled temperature lagged by 2 days. \\
$w_{b,288,t}$ & 288 & Scaled temperature lagged by 3 days. \\
$w^+_{b,t}$ & & Maximum scaled temperature over last 24 hours. \\
$w^-_{b,t}$ & & Minimum scaled temperature over last 24 hours. \\
$\bar{w}_{b,t}$ & & Average scaled temperature over last 3 days. \\
$y_{b,96,t}$ & 96 & Scaled actual demand lagged by 1 day. \\
$y_{b,192,t}$ & 192 & Scaled actual demand lagged by 2 days. \\
$y_{b,672,t}$ & 672 & Scaled actual demand lagged by 1 week. \\
\bottomrule
\end{tabular}
\end{table}

<!-- Table: (\#tab:weather-vars) Predictor variables evaluated during feature selection stage when determining $\mathcal{P}_t$. -->

<!-- Variable $x_{b,i,t}$ | Lag (15-minute periods) | Description -->
<!-- ----------------|---------|------------------------------------------------- -->
<!-- $w_{b,0,t}$     | 0       | Scaled current temperature. -->
<!-- $w_{b,12,t}$    | 12      | Scaled temperature lagged by 3 hours. -->
<!-- $w_{b,24,t}$    | 24      | Scaled temperature lagged by 6 hours. -->
<!-- $w_{b,48,t}$    | 48      | Scaled temperature lagged by 12 hours. -->
<!-- $w_{b,96,t}$    | 96      | Scaled temperature lagged by 24 hours. -->
<!-- $w_{b,192,t}$   | 192     | Scaled temperature lagged by 2 days. -->
<!-- $w_{b,288,t}$   | 288     | Scaled temperature lagged by 3 days. -->
<!-- $w^+_{b,t}$     |         | Maximum scaled temperature over last 24 hours. -->
<!-- $w^-_{b,t}$     |         | Minimum scaled temperature over last 24 hours. -->
<!-- $\bar{w}_{b,t}$ |         | Average scaled temperature over last 3 days. -->
<!-- $y_{b,96,t}$    | 96      | Scaled actual demand lagged by 1 day. -->
<!-- $y_{b,192,t}$   | 192     | Scaled actual demand lagged by 2 days. -->
<!-- $y_{b,672,t}$   | 672     | Scaled actual demand lagged by 1 week. -->

@@

@@

When comparing these metrics in Section \@ref(forecasting-accuracy), we find that the SSC and SSCATTR models produce the best point forecasts. To establish that this result is statistically significant we also carry out Diebold-Mariano tests against the ILR model in Section \@ref(diebold-mariano-test).

@@

(ref:accuracy-results) Forecasting accuracy measures for each model across the entire day, business hours (7:00 am to 7:00 pm) and non-business hours (7:00 pm to 7:00 am).
